PubCrawl: A Publication Search Engine

### 2012-05-18 report/paper.tex
Reorganize stuff

To evaluate the quality of PubCrawl results, we performed a preliminary user
study comparing the quality of PubCrawl results with those from Google Scholar,
Microsoft Academic Search, ACM Digital Library and CiteSeer.

@@

We obtained information about important papers on 6 topics from experts in the
respective areas. We then manually picked weights, given in Table \ref{weights}
that gave good results for all 6 topics.

@@

>>>>

@@

To evaluate the quality of PubCrawl results, we performed a preliminary user
study comparing the quality of PubCrawl results with those from Google Scholar,
Microsoft Academic Search, ACM Digital Library and \citeseer. We obtained
information about important papers on 6 topics from experts in the respective
areas. We then manually picked weights shown in Table \ref{weights} that gave
good results for all 6 topics.

@@

\subsection{Results}
